Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-09 Docs/IJES/journal.tex
What is the meaning of "Aeq" and "beq" in Eq. 1?

Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances as defined in~\cite{Rao2009}. There is no single method available for efficiently solving all optimization problems, according to~\cite{Rao2009}. The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables. A particular case of linear programming is ILP, in which the variables can assume just integer values. Eq.~\ref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors or matrixes that describe the constraints

@@

\vspace{-5 mm}
Consequently, the second approach aims to remove the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}. This approach could potentially lead to great performance improvements, but as ESBMC checks for each step almost at the same rate, the processor does not remain idle for a longer period and thus there is almost no optimization.

>>>>

Optimization is the act of obtaining the best result ({\it i.e.}, the optimal solution) under given circumstances as defined in~\cite{Rao2009}. There is no single method available for efficiently solving all optimization problems, according to~\cite{Rao2009}. The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables. A particular case of linear programming is ILP, in which the variables can assume just integer values. Eq.~\ref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors from the objective function, while $Aeq$ and $beq$ are matrices that describe the linear equality constraints

@@

Consequently, the second approach aims to remove the idle time from the parallel loops, by creating workers inside threads so that the next step is immediately executed if there is a processing core available, as shown in Fig.~\ref{ESBMC-Multi-core-Optimized-Sequential-Approach}. This approach could potentially lead to great performance improvements, but as ESBMC checks for each step almost at the same rate, the processor does not remain idle for a longer period and thus there is almost no optimization.
